---
title: "dada2 filtering results"
header-includes: #allows you to add in your own Latex packages
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h

output:
  pdf_document:
    fig_caption: true
    keep_tex: true
    latex_engine: pdflatex
  html_document:
    df_print: paged
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(out.extra = '')
#knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_knit$set(root.dir = "../")
```
# dada2 filtering reads

The first stage of the dada2 pipeline is filtering and trimming of reads. The number of reads
that remain for downstream analysis is dependent on the parameters that were set for filtering
and trimming. In most cases it would be expected that the vast majority of reads will remain
after this step. It is noteworthy that dada2 does not accept any "N" bases and so will remove
reads if there is an N in the sequence.

```{r include=FALSE, echo=FALSE}
library(ggplot2)
library(gridExtra)
library(dplyr)
```

## Number of reads input/output during filtering and trimming

Below is a summary of the number of input reads and the number of output reads for each sample.

```{r filtering, fig.cap='Number of input and output reads during filtering step', fig.height=5, fig.width=8,  echo=FALSE, message=FALSE}

infiles = list.file()[grep("filtered.dir/*summary.tsv")]
dfs <- list()
for (i in 1:length(infiles)){
    dfs[i] <- read.csv(infiles[i], headerr=T, stringsAsFactors=F, sep="\t")
}



```
